### 2008-08-14 doc/glite_gateway/glite_gateway.tex
Layout and biblography corrections

\begin{tabular}{rl}
\resizebox*{3cm}{!}{\includegraphics{logo-knowarc.png}}
\end{tabular}

@@

{\centering \large Ivan Marton\footnote{martoni@niif.hu} \large \par}
{\centering \large Peter Stefan\footnote{stefan@niif.hu} \large \par}

@@

An overview of the preferred soulution is presented in figure \ref{fig:Chart 1}. The user will be able to express the job requirements in the job description document using any of the xRSL\cite{xrsl}, JDL or JSDL\cite{jsdl} languages. The ARC client library will perform an automatic transformation. The gLite gateway functionality integrated into the ARCLIB, thus into the ARC client allow the user to transparently access gLite computing resources via the usual ARC command line tools. The gLite modules perform authentication, credential delagation and job submission to the CREAM2 CE. The CREAM2 CE may perform the necessary input file download from the different storage elements. The library module gets job information through CREAM2 and sends management commands, like kill a job or undelegate credentials. Note that not all the functionality described in the overview figure is implemented yet, for the current limitations see section \ref{Current limitations}!\par

@@

\caption{\label{fig:Chart 1}This chart illustrates how the ARC1$\rightarrow$gLite gateway library module based approach works.}}

@@

\centering{\resizebox{255px}{!}{\includegraphics{JobDescriptionExample-XRSLInput.jpg}}
\caption{\label{fig:Chart 1}The figure shows how the different classes participating in the job description translation process interrelate in an example about xRSL parsing.}}

>>>>

\begin{tabular}{rl}
\resizebox*{3cm}{!}{\includegraphics{ng-logo.png}}
&\parbox[b]{2cm}{\textbf \it {\hspace*{-1.5cm}NORDUGRID\vspace*{0.5cm}}}
\end{tabular}

@@

{\centering \large Iv\'{a}n M\'{a}rton\footnote{martoni@niif.hu} \large \par}
{\centering \large P\'{e}ter Stef\'{a}n\footnote{stefan@niif.hu} \large \par}

@@

An overview of the preferred soulution is presented in figure \ref{fig:Chart1}. The user will be able to express the job requirements in the job description document using any of the xRSL\cite{xrsl}, JDL or JSDL\cite{jsdl} languages. The ARC client library will perform an automatic transformation. The gLite gateway functionality integrated into the ARCLIB, thus into the ARC client allow the user to transparently access gLite computing resources via the usual ARC command line tools. The gLite modules perform authentication, credential delagation and job submission to the CREAM2 CE. The CREAM2 CE may perform the necessary input file download from the different storage elements. The library module gets job information through CREAM2 and sends management commands, like kill a job or undelegate credentials. Note that not all the functionality described in the overview figure is implemented yet, for the current limitations see section \ref{Current limitations}!\par

@@

\caption{\label{fig:Chart1}This chart illustrates how the ARC1$\rightarrow$gLite gateway library module based approach works.}}

@@

\centering{\resizebox{255pt}{!}{\includegraphics{JobDescriptionExample-XRSLInput.jpg}}
\caption{\label{fig:Chart2}The figure shows how the different classes participating in the job description translation process interrelate in an example about xRSL parsing.}}
